---
title: "Evaluation"
author: "Krishna"
date: "4/22/2020"
output: html_document
---

```{r}
library(magrittr)
library(dplyr)
library(data.table) # Faster reading speeds for csv files (fread)
```

## Loading the Test Datasets

```{r}
test_scenario3 <- fread("C:/Users/krish/Desktop/Subjects/Spr-20/Adv Data Mining/Group Project/test_scenario3.csv", data.table = F, colClasses = c("character"))
test_scenario1_2 <- fread("C:/Users/krish/Desktop/Subjects/Spr-20/Adv Data Mining/Group Project/test_scenario1_2.csv", data.table = F, colClasses = c("character"))
```

## Getting Columns Specific to Scenario 1 & 2

```{r}
requested_loan_1_2 <- test_scenario1_2 %>% select(requested_loan)
```

## Getting Columns Specific to Scenario 3

```{r}
requested_loan_3 <- test_scenario3 %>% select(requested_loan)
prop_int_rate <- test_scenario3 %>% select(Proposed_Intrest_Rate)
```

## Recoding The Variables as Numeric

```{r}
requested_loan_1_2 <- requested_loan_1_2 %>% mutate_all(as.numeric)
requested_loan_3 <- requested_loan_3 %>% mutate_all(as.numeric)
prop_int_rate <- prop_int_rate %>% mutate_all(as.numeric)
```

## Loading PD and LGD of Customers in Test Set

```{r}
LGD <- read.csv("C:/Users/krish/Desktop/Subjects/Spr-20/Adv Data Mining/Group Project/LGD.csv")
PD <- read.csv("C:/Users/krish/Desktop/Subjects/Spr-20/Adv Data Mining/Group Project/PD.csv")
```


## Evaluating Customers in Scenario 1

CAPITAL <- $1.4B

```{r}
sc_1 <- test_scenario1_2 %>%
  select(id) %>%
  bind_cols(requested_loan_1_2, PD, LGD) %>%
  rename(LGD = x) %>%
  mutate(
    Oppurtunity = requested_loan * 0.0432 * 5 * (1 - PD),
    Risk = requested_loan * PD *  LGD
  )

summary(sc_1)
```

## Total Requested Loan where Oppurtunity >= Risk in Scenario 1

```{r}
sc_1 %>%
  mutate(loan_approval = ifelse(Oppurtunity >= Risk, 1, 0)) %>%
  mutate_at(c("loan_approval"), as.factor) %>%
  filter(loan_approval == 1) %>%
  select(requested_loan) %>%
  transmute(total_requested_loan = format(sum(.), big.mark = ",", scientific = F)) %>%
  head(1)
```

## Final Descision on Customer Loan Approval in Scenario 1

```{r}
sc_1 %>%
  mutate(loan_approval = ifelse(Oppurtunity >= Risk, 1, 0)) %>%
  select(loan_approval) %>%
  write.csv(file = "C:/Users/krish/Desktop/Subjects/Spr-20/Adv Data Mining/Group Project/G7_S1.csv", row.names = F)
```

## Evaluating Customers in Scenario 2

Budget <- $450M

```{r}
sc_2 <- test_scenario1_2 %>%
  select(id) %>%
  bind_cols(requested_loan_1_2, PD, LGD) %>%
  rename(LGD = x) %>%
  mutate(
    Oppurtunity = requested_loan * 0.0432 * 5 * (1 - PD),
    Risk = requested_loan * PD *  LGD
  )
```

## Final Descision on Customer Loan Approval in Scenario 2

```{r}
sc_2 %>%
  mutate(loan_approval = ifelse(Oppurtunity >= Risk, 1, 0)) %>%
  select(loan_approval) %>%
  write.csv(file = "C:/Users/krish/Desktop/Subjects/Spr-20/Adv Data Mining/Group Project/G7_S2.csv", row.names = F)
```



## Evaluating Customers in Scenario 3

Budget <- $1.4B

```{r}
sc_3 <- test_scenario3 %>%
  select(id) %>%
  bind_cols(requested_loan_1_2, prop_int_rate, PD, LGD) %>%
  rename(LGD = x) %>%
  mutate(
    Oppurtunity = requested_loan * Proposed_Intrest_Rate * 5 * (1 - PD),
    Risk = requested_loan * PD *  LGD
  )

head(sc_3)
```

```{r}
sc_3 %>% select(Proposed_Intrest_Rate) %>% summary()
```

## Total Requested Loan where Oppurtunity >= Risk in Scenario 3

```{r}
sc_3 %>%
  mutate(loan_approval = ifelse(Oppurtunity >= Risk, 1, 0)) %>%
  mutate_at(c("loan_approval"), as.factor) %>%
  filter(loan_approval == 1) %>%
  select(requested_loan) %>%
  transmute(total_requested_loan = format(sum(.), big.mark = ",", scientific = F)) %>%
  head(1)
```

## Total Sum of Oppurtunity in Scenario 3

```{r}
sc_3 %>%
  mutate(loan_approval = ifelse(Oppurtunity >= Risk, 1, 0)) %>%
  mutate_at(c("loan_approval"), as.factor) %>%
  filter(loan_approval == 1) %>%
  select(Oppurtunity) %>%
  transmute(total_oppurtunity = format(sum(.), big.mark = ",", scientific = F)) %>%
  head(1)
```

## PD at 0.5 in Scenario 3

```{r}
sc_3 %>%
  mutate(default = ifelse(PD >= 0.5, 1, 0)) %>%
  mutate_at(c("default"), as.factor) %>%
  select(default) %>%
  summary()
```

```{r}
sc_3 %>%
  mutate(default = ifelse(PD >= 0.5, 1, 0)) %>%
  mutate_at(c("default"), as.factor) %>%
  filter(default == 0) %>%
  select(Oppurtunity) %>%
  transmute(total_oppurtunity = format(sum(.), big.mark = ",", scientific = F)) %>%
  head(1)
```

## PD at 0.1 in Scenario 3

```{r}
sc_3 %>%
  mutate(default = ifelse(PD >= 0.1, 1, 0)) %>%
  mutate_at(c("default"), as.factor) %>%
  select(default) %>%
  summary()
```

```{r}
sc_3 %>%
  mutate(default = ifelse(PD >= 0.1, 1, 0)) %>%
  mutate_at(c("default"), as.factor) %>%
  filter(default == 0) %>%
  select(Oppurtunity) %>%
  transmute(total_oppurtunity = format(sum(.), big.mark = ",", scientific = F)) %>%
  head(1)
```

## Final Descision on Customer Loan Approval in Scenario 3

```{r}
sc_3 %>%
  mutate(default = ifelse(PD >= 0.1, 1, 0)) %>%
  mutate(loan_approval = ifelse(default == 0, 1, 0)) %>%
  select(loan_approval) %>%
  write.csv(file = "C:/Users/krish/Desktop/Subjects/Spr-20/Adv Data Mining/Group Project/G7_S3.csv", row.names = F)
```





